Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2018-12-13 Manuscript/manuscript.Rmd
edits

To establish the data for modeling, the genome was binned into equally sized intervals (Figure 18 C). In order for a more systematic approach, the binning process was performed at the same resolution of the contact matrix that the domain data was obtained from. For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals. The same processes was repeated for each of the other three resolutions. Again, operating systematically, we flanked the boundary coordinates on either side by a unit corresponding to the resolution of the particular domain data. For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb. The same process was repeated for the other three resolutions. A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary. Otherwise, the bin was labeled as not containing a boundary (Y=0).

>>>>

To establish the data for modeling, the genome was binned into equally sized intervals (Figure 18 C). For a more systematic approach, the binning process was performed using the coordinates of the sparse contact matrix of the corresponding resolution. For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals using the coordinates of a 5kb resolution contact matrix. The same processes was repeated for each of the other three resolutions. Again, operating systematically, we flanked the boundary coordinates on either side by a unit corresponding to the resolution of the particular domain data. For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb. The same process was repeated for the other three resolutions. A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary. Otherwise, the bin was labeled as not containing a boundary (Y=0).
